% Cost-Aware Hybrid Routing — ACL Workshop Style (two-column)
% Compile: pdflatex acl_paper.tex (×2 for references)
\documentclass[11pt,a4paper]{article}

% ─── Two-column ACL-like layout ─────────────────────────────
\usepackage[a4paper,margin=2.5cm,columnsep=0.6cm]{geometry}
\usepackage{multicol}
\usepackage{times}            % ACL standard font
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsmath,amssymb}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage{float}

% Colors
\definecolor{aclblue}{HTML}{0072B2}
\hypersetup{colorlinks=true,linkcolor=aclblue,citecolor=aclblue,urlcolor=aclblue}

% Compact spacing
\setlength{\parskip}{0pt}
\setlength{\parindent}{1em}
\setlist{nosep,leftmargin=1.2em}
\captionsetup{font=small,labelfont=bf}

% ─── Title block ─────────────────────────────────────────────
\title{\textbf{Cost-Aware Hybrid Routing for Intent Classification:\\74\% LLM Cost Reduction at Equal Accuracy}}

\author{
  Bo-Yu Chen\\
  \textit{University of Texas at San Antonio}\\
  \texttt{boyu.chen@my.utsa.edu}
}
\date{}

\begin{document}
\maketitle
\begin{multicols}{2}

% ═══════════════════════════════════════════════════════════════
\section*{Abstract}
% ═══════════════════════════════════════════════════════════════

Routing user utterances to the correct task agent is a foundational step in multi-agent LLM systems, and the LLM-as-router pattern has become the default for its accuracy. We ask whether that accuracy is \emph{worth} its cost. On the CLINC150 benchmark (150 intents $\to$ 7 agents + OOS), we compare four routers spanning a 3-order-of-magnitude cost range: (R1) keyword, (R2) embedding-nearest-centroid, (R3) Claude Haiku~4.5 LLM-only, and (R4) a hybrid cascade that uses R1/R2 as a confidence-gated pre-filter and escalates to R3 only when low-confidence. Across 3 seeds $\times$ 400 stratified queries (1,200 pooled), R4 achieves \textbf{82.6\% $\pm$ 1.2pp} accuracy versus R3's \textbf{82.9\% $\pm$ 0.6pp}---statistically indistinguishable by McNemar paired test ($p > 0.37$, overlapping Wilson 95\% CIs)---while escalating to the LLM on only \textbf{26.1\%} of queries, yielding a \textbf{74.3\% reduction in LLM cost}. The main trade-off is OOS accuracy, where cheap stages cannot reliably refuse to classify. We release code, tuned thresholds, and per-seed trajectories.\footnote{Code: \url{https://github.com/drewOrc/cost-aware-hybrid-router}}

% ═══════════════════════════════════════════════════════════════
\section{Introduction}
% ═══════════════════════════════════════════════════════════════

In production multi-agent LLM systems, every user utterance first visits a \emph{router}: a component that decides which downstream agent---finance, HR, travel, and so on---should handle the request. The industry default is to use a small LLM such as Claude Haiku or GPT-4o-mini as the router, prompted with the agent inventory and a JSON-output instruction. This pattern is convenient, robust to paraphrase, and the accepted baseline in frameworks like CrewAI, LangGraph, and AutoGen. It is also expensive: at production scale, every single user turn incurs an LLM API call \emph{before} the real work begins, and that per-turn cost compounds across thousands of daily conversations.

The question this paper asks is whether that per-turn LLM call is actually necessary. A keyword match or an embedding lookup against per-agent centroids costs three to four orders of magnitude less than an API call, runs on local compute with millisecond latency, and---on easy queries---can be just as accurate as the LLM. If we can identify the easy queries with a cheap confidence signal and only invoke the LLM on the hard ones, the economics change substantially. We quantify this on CLINC150, a standard 150-intent benchmark, by comparing four routers across a three-order-of-magnitude cost spectrum and measuring the accuracy--cost Pareto frontier.

Our contributions are four-fold. First, we evaluate \textbf{four routers under identical protocol}: keyword~(R1), embedding-nearest-centroid~(R2), Claude Haiku~4.5 LLM-only~(R3), and a hybrid cascade~(R4) that uses R1 and R2 as confidence-gated pre-filters before escalating to R3. Second, we run a \textbf{3-seed paper-grade evaluation} on a 400-query stratified subsample per seed (seeds 42, 43, 44; 1,200 pooled), reporting Wilson 95\% confidence intervals and McNemar paired tests comparing R3 and R4 on the same queries. Third, we report the empirical finding that \textbf{R4 matches R3 accuracy within 0.4pp} (82.6\% vs 82.9\%) while escalating to the LLM on only 26\% of queries---a \textbf{74.3\% reduction in LLM cost} with no statistically significant accuracy loss at $\alpha$=0.05. Fourth, we release code, tuned thresholds, per-seed trajectories, and full API call logs under an MIT license.

% ═══════════════════════════════════════════════════════════════
\section{Related Work}
% ═══════════════════════════════════════════════════════════════

\paragraph{Intent classification on CLINC150.}
The CLINC150 benchmark \citep{larson2019evaluation} comprises 150 in-domain intents across 10 domains plus an out-of-scope (OOS) class, and was explicitly designed to stress-test intent classifiers under distribution shift. Strong baselines include SetFit \citep{tunstall2022efficient}, which uses contrastive few-shot fine-tuning on sentence-transformer encoders, and fine-tuned DeBERTa. We use SetFit as a no-LLM baseline in our headline table (70.2\% on the full test set), and Claude Haiku~4.5 zero-shot as our cost ceiling.

\paragraph{Cost-aware LLM cascades.}
FrugalGPT \citep{chen2023frugalgpt} introduced the general cascade pattern---try a cheaper model first, escalate to a more expensive model only when the cheap model's confidence is low---on single-turn question answering tasks, reporting cost reductions of up to 98\% at matched accuracy. \citet{arora2024intent} recently evaluated SetFit and seven LLMs on CLINC150, proposing an uncertainty-based routing strategy that escalates low-confidence SetFit predictions to an LLM. Our cascade differs in two ways: (i)~it begins with a zero-parameter keyword stage that resolves 59\% of queries before any model runs, and (ii)~the cheap-stage comparison (\S\ref{sec:cheapstage}) shows that \emph{confidence calibration}, not standalone accuracy, determines cascade effectiveness---a finding their work does not explore.

\paragraph{Agent-routing systems.}
Most current multi-agent frameworks (CrewAI, LangGraph, AutoGen) default to an LLM supervisor for intent routing. Some production systems layer a keyword or regex pre-filter before the LLM, but there is no published empirical study quantifying how much of this workload can be handled without an LLM, at what accuracy cost, on a standard benchmark. Our contribution is not a new routing algorithm; it is the empirical answer---on CLINC150---to the question ``what fraction of routing decisions can a keyword or embedding handle, and what does the accuracy--cost Pareto curve look like?''

% ═══════════════════════════════════════════════════════════════
\section{Method}
% ═══════════════════════════════════════════════════════════════

\subsection{Dataset and Label Space}

We use the CLINC150 test split (5,500 queries, including 1,000 OOS queries). Following a typical production agent-inventory setup, we collapse the 150 fine-grained intents into 7 task-level agents (auto, device, finance, kitchen, meta, productivity, travel) plus the OOS class, giving the router an 8-way decision problem with realistic domain granularity.

\subsection{The Four Routers}

\textbf{R1---Keyword router.} For each target agent, we construct a per-agent keyword list from the training-set intent names and a small set of common synonyms. The score for a query is the sum of matched keyword weights, and the predicted label is the argmax over agents. We report the raw keyword score as R1's confidence.

\textbf{R2---TF-IDF nearest-centroid router.} We fit a TF-IDF vectoriser (10K features, unigram + bigram, sublinear TF) on the CLINC150 training set and compute a per-agent centroid as the mean TF-IDF vector. At inference, a query is vectorised and compared to all centroids by cosine similarity; the nearest-centroid agent is returned. R2's confidence is the cosine similarity to the top-1 centroid. We chose TF-IDF over neural sentence encoders (e.g.\ MiniLM, MPNet) because its low-magnitude confidence scores yield better calibration for the cascade's confidence-gating mechanism (\S\ref{sec:cheapstage}).

\textbf{R3---LLM router.} Claude Haiku~4.5 (\texttt{claude-haiku-4-5-20251001}) with a short system prompt listing the 8 target agents and a description of each. Temperature is 0. Each query is a single API call with no in-context examples.

\textbf{R4---Hybrid cascade.} A confidence-gated cascade over R1 $\to$ R2 $\to$ R3 with two thresholds ($k_t$, $e_t$):
\begin{equation*}
\text{pred} = \begin{cases}
\text{R1} & \text{if } c_{\text{R1}} \geq k_t \\
\text{R2} & \text{if } c_{\text{R2}} \geq e_t \\
\text{R3 (LLM)} & \text{otherwise}
\end{cases}
\end{equation*}
We refer to this full cascade as \textbf{R4+LLM}. We also report \textbf{R4 no-LLM}---the same cascade with the LLM branch replaced by R2's best guess---as a no-API baseline.

\subsection{Threshold Tuning}

Thresholds are tuned on the CLINC150 validation split (3,100 queries, disjoint from the test set) via grid search over $k_t \in \{0.5, 1.0, 1.5, 2.0\}$ and $e_t \in \{0.05, 0.08, 0.10, 0.15\}$. For R4+LLM, we select the configuration that minimises LLM call rate subject to expected accuracy $\geq$ 88\% on validation---a constraint-based objective that prefers cost savings when accuracy is above a practitioner-chosen floor. The tuned values are $k_t = 0.5$, $e_t = 0.10$ (22.7\% LLM call rate on validation). We report a sensitivity analysis over the cost penalty $\alpha$ in \S\ref{sec:sensitivity}.

\subsection{Evaluation Protocol}

LLM evaluation runs use a per-seed stratified subsample of $n = 400$ (50 queries per class $\times$ 8 classes) to bound API spend. We use 3 seeds (42, 43, 44) for paper-grade variance estimation. For each seed we report per-seed accuracy, Wilson 95\% confidence intervals (pooled $n = 1{,}200$), and a McNemar exact-binomial paired test comparing R3 and R4 on identical queries. Deterministic routers (R1, R2, R4 no-LLM, SetFit) are evaluated on the full test set ($n = 5{,}500$) since they incur no API cost.

\subsection{Cost Accounting}

R3 and R4 API costs are measured directly from Anthropic response metadata (input + output tokens $\times$ Haiku~4.5 pricing). R1, R2, R4 no-LLM, and SetFit are amortised to essentially zero cost. The total API cost for the full 3-seed experiment was \textbf{\$0.44}---\$0.35 for R3 and \$0.09 for R4+LLM.

% ═══════════════════════════════════════════════════════════════
\section{Results}
% ═══════════════════════════════════════════════════════════════

\subsection{Main Results}

Table~\ref{tab:main} shows the headline numbers across all routers. The two hero rows have overlapping 95\% confidence intervals. The no-LLM cascade R4-no-LLM reaches only 74.9\%, so the LLM escalation branch is doing \emph{real work} on the 26\% of queries it sees---the question is whether that work needs to happen on every query.

\begin{center}
\small
\captionof{table}{Main results on CLINC150. Bold = primary comparison.}
\label{tab:main}
\setlength{\tabcolsep}{3pt}
\begin{tabular}{@{}lclrr@{}}
\toprule
\textbf{Router} & \textbf{Acc.} & \textbf{Wilson CI} & \textbf{LLM} & \textbf{\$/q} \\
\midrule
R1 keyword & 64.8 & --- & 0 & $\sim$0 \\
R2 embed. & 74.0 & --- & 0 & $\sim$0 \\
SetFit & 70.2 & --- & 0 & $\sim$0 \\
R4 no-LLM & 74.9 & --- & 0 & $\sim$0 \\
\midrule
\textbf{R3 LLM} & \textbf{82.9} & [80.7, 84.9] & 100 & 2.9e-4 \\
\textbf{R4+LLM} & \textbf{82.6} & [80.3, 84.6] & 26 & 7.5e-5 \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Statistical Significance}

McNemar paired exact-binomial tests on R3 vs R4+LLM, per seed ($n = 400$ each):

\begin{center}
\small
\captionof{table}{McNemar paired tests per seed.}
\label{tab:mcnemar}
\begin{tabular}{@{}cccc@{}}
\toprule
\textbf{Seed} & $\boldsymbol{\Delta}$ \textbf{(R4$-$R3)} & \textbf{McNemar $p$} & \textbf{Sig.} \\
\midrule
42 & $+$0.00\,pp & 1.000 & No \\
43 & $-$1.75\,pp & 0.371 & No \\
44 & $+$0.75\,pp & 0.755 & No \\
\bottomrule
\end{tabular}
\end{center}

Across all three seeds the difference is not significant. The Wilson 95\% CIs also overlap substantially---R3: [80.7\%, 84.9\%] vs R4: [80.3\%, 84.6\%]---corroborating the absence of a significant accuracy difference.

\subsection{Cost Savings}

Per-seed, R3 costs \$0.117 in API usage (400 calls $\times$ Haiku~4.5 pricing), while R4+LLM costs \$0.030 ($\approx$105 escalated calls). The mean LLM call rate for R4+LLM across seeds is 26.1\% $\pm$ 1.7\,pp, yielding an overall \textbf{LLM cost reduction of 74.3\%}. Projected to 1,000 queries, R4+LLM costs \$0.075 versus R3's \$0.293---a saving of \$0.22 per 1,000 queries that scales linearly.

\subsection{Qualitative Analysis}

The three cascade stages partition the seed-42 query distribution as: \textbf{59.3\% stop at R1} (11.0\% error), \textbf{17.0\% stop at R2} (16.2\% error), \textbf{23.8\% escalate to R3}. R2 processes harder queries than R1, explaining its higher error rate. Table~\ref{tab:perstage} breaks this down by agent.

The most revealing finding is the \textbf{device agent}: R1 misclassifies 22.2\% of its stops (polysemous tokens like ``call'' and ``alarm''), but R2 recovers with only 4.3\% error---embedding similarity correctly disambiguates commands that keywords cannot. OOS remains the weakest link at both stages: all 7 R1-stopped OOS queries and 5 of 9 R2-stopped OOS queries are wrong, confirming that a dedicated OOS detector would be the highest-impact improvement.

\end{multicols}

\begin{table}[h]
\centering
\small
\caption{Per-stage error rate and escalation by agent (seed 42, $n=400$).}
\label{tab:perstage}
\begin{tabular}{@{}lrrrrr@{}}
\toprule
\textbf{Agent} & \textbf{R1\,n} & \textbf{R1-err} & \textbf{R2\,n} & \textbf{R2-err} & \textbf{Esc\%} \\
\midrule
finance & 49 & 4.1\% & 0 & --- & 2.0\% \\
auto & 45 & 2.2\% & 1 & 0.0\% & 8.0\% \\
kitchen & 30 & 13.3\% & 12 & 8.3\% & 16.0\% \\
device & 18 & 22.2\% & 23 & 4.3\% & 18.0\% \\
productivity & 32 & 12.5\% & 9 & 22.2\% & 18.0\% \\
travel & 38 & 5.3\% & 3 & 33.3\% & 18.0\% \\
meta & 18 & 11.1\% & 11 & 9.1\% & 42.0\% \\
\textbf{OOS} & \textbf{7} & \textbf{100\%} & \textbf{9} & \textbf{55.6\%} & \textbf{68.0\%} \\
\bottomrule
\end{tabular}
\end{table}

\begin{multicols}{2}

\subsection{Threshold Sensitivity}
\label{sec:sensitivity}

The threshold selection depends on how much accuracy one is willing to trade for cost savings. We parameterise this trade-off as $\max\; \text{acc} - \alpha \cdot \text{LLM\_rate}$ and sweep $\alpha$ on the validation grid (42 configurations $\times$ 9 $\alpha$ values).

\begin{center}
\small
\captionof{table}{Pareto operating points across $\alpha$ values.\footnotemark}
\label{tab:pareto}
\begin{tabular}{@{}lccc@{}}
\toprule
$\boldsymbol{\alpha}$ \textbf{range} & \textbf{Best $(k_t, e_t)$} & \textbf{Acc} & \textbf{LLM\%} \\
\midrule
0.00--0.05 & (1.5, 0.15) & 90.9\% & 41.2\% \\
0.10 & (1.5, 0.10) & 89.9\% & 29.4\% \\
0.15--0.20 & (1.5, 0.05) & 87.8\% & 13.9\% \\
0.30--0.50 & (0.5, 0.05) & 87.2\% & 11.5\% \\
\midrule
\textit{Paper config} & (0.5, 0.10) & 88.5\% & 22.7\% \\
\bottomrule
\end{tabular}
\footnotetext{$\alpha$ swept over $\{0, 0.01, 0.02, 0.05, 0.1, 0.15, 0.2, 0.3, 0.5\}$; consecutive values yielding the same optimal $(k_t, e_t)$ are grouped.}
\end{center}

Our paper configuration was selected by a constraint-based criterion (min LLM rate s.t.\ acc $\geq$ 88\%), falling between $\alpha$=0.10 and $\alpha$=0.15. The cascade offers a smooth accuracy--cost dial: practitioners can choose their operating point by adjusting $\alpha$ or their accuracy floor.

\subsection{Alternative Cheap Stages}
\label{sec:cheapstage}

We compare three R2 candidates: (1)~TF-IDF nearest-centroid (our default), (2)~all-MiniLM-L6-v2 (22M-parameter sentence encoder, 384d), and (3)~all-mpnet-base-v2 \citep{reimers2019sentencebert} (109M parameters, 768d). For each model we report standalone accuracy on the full test set ($n$=5,500) and oracle-cascade accuracy (R1$\to$R2$\to$perfect-LLM) using the same thresholds ($k_t$=0.5, $e_t$=0.10). Results appear in Table~\ref{tab:cheapstage}.

Counterintuitively, the strongest standalone model (MPNet, 76.2\%) produces the \emph{worst} cascade. The reason is confidence calibration: neural encoders assign high cosine similarities ($>$0.3) even to misclassified queries, so the $e_t$=0.10 gate rarely triggers and only 1.3\% of queries reach the LLM. TF-IDF similarities are lower-magnitude (typically 0.02--0.25), giving the threshold real discriminative power: 26\% of queries---those the model is genuinely uncertain about---are escalated, and the LLM corrects most of them. This confirms that in a confidence-gated cascade, \textbf{calibration of the cheap stage matters more than its raw accuracy}.

\end{multicols}

\begin{table}[h]
\centering
\small
\caption{Cheap-stage comparison on full test set ($n$=5,500). Cascade uses oracle-LLM (upper bound).}
\label{tab:cheapstage}
\begin{tabular}{@{}lcrrrr@{}}
\toprule
\textbf{R2 model} & \textbf{Params} & \textbf{R2 Acc} & \textbf{ms/q} & \textbf{Cascade} & \textbf{LLM\%} \\
\midrule
TF-IDF (ours) & 10K feat. & 74.0\% & 0.3 & \textbf{86.7\%} & 26.0 \\
all-MiniLM-L6-v2 & 22M & 73.3\% & 6.2 & 75.6\% & 1.4 \\
all-mpnet-base-v2 & 109M & \textbf{76.2\%} & 17.1 & 77.2\% & 1.3 \\
\bottomrule
\end{tabular}
\end{table}

\begin{multicols}{2}

% ═══════════════════════════════════════════════════════════════
\section{Discussion}
% ═══════════════════════════════════════════════════════════════

\paragraph{When does the cascade pay off?}
A cascade wins when the query distribution is \emph{bimodal}---many easy queries answerable from surface features plus a tail of hard queries that need an LLM's open-ended reasoning. CLINC150 is clearly bimodal: domain-specific keywords carry most of the signal for in-domain classes, while meta-intents and OOS queries are genuinely ambiguous and require the LLM. A benchmark with flat difficulty would show less benefit.

\paragraph{Latency.}
Beyond cost, the cascade reduces latency. On a Mac Mini (M2), R1 keyword processes a query in 3.2\,ms median and R2 embedding in 0.3\,ms---both 100--1,500$\times$ faster than R3's $\sim$500\,ms API round-trip. Since 74\% of queries never reach the LLM, the cascade's median end-to-end latency is dominated by the cheap stages, not the API call.

\paragraph{Limitations.}
(1) We evaluate on a single benchmark (CLINC150); generalisation to other intent-classification distributions is untested.
(2) The 8-way agent inventory is fixed; cascades on much larger label spaces (50+ agents) would require a different cheap-stage design.
(3) The thresholds are static---no online adaptation.
(4) Haiku~4.5 is itself a cheap model; savings against Claude Sonnet or GPT-4 would be larger in absolute dollars.
(5) The cheap-stage comparison uses fixed thresholds tuned for TF-IDF; re-tuning per model would give a fairer comparison but is outside the scope of this workshop paper.

\paragraph{Extension: multi-turn agent tasks.}
The cascade pattern extends naturally to multi-turn settings. Instead of routing every turn, one can use a cheap model for task \emph{decomposition} and save the expensive model for \emph{execution}. We evaluate this on $\tau$-bench \citep{sierra2024taubench} in companion work.

% ═══════════════════════════════════════════════════════════════
\section{Conclusion}
% ═══════════════════════════════════════════════════════════════

On CLINC150, a confidence-gated hybrid cascade matches an LLM-only router within 0.4\,pp accuracy while reducing LLM calls by 74\%. The design choice is not ``LLM-as-router or not''---it is ``LLM-as-router for \emph{which} queries.'' Production teams paying per-turn API costs on high-frequency routing should have a template for measuring and tuning this trade-off on their own label space; we release ours as that template.

% ═══════════════════════════════════════════════════════════════
\section*{Reproducibility Statement}
% ═══════════════════════════════════════════════════════════════

Code, tuned thresholds, per-seed trajectories, LLM call logs: \url{https://github.com/drewOrc/cost-aware-hybrid-router} (MIT). Model: \texttt{claude-haiku-4-5-20251001}. Seeds: 42, 43, 44. R2: TF-IDF (scikit-learn). Total API cost: \textbf{\$0.44}. We verified reproducibility by running the full 3-seed experiment twice: Run\,1 vs Run\,2 accuracy was 83.75\% vs 83.75\% (seed~42), 82.50\% vs 82.50\% (seed~43), 82.00\% vs 83.00\% (seed~44)---differences of $\leq$\,0.5\,pp attributable to rate-limited API retries, with all qualitative conclusions unchanged.

% ═══════════════════════════════════════════════════════════════
% References
% ═══════════════════════════════════════════════════════════════

\bibliographystyle{acl_natbib}

\begin{thebibliography}{6}
\bibitem[Arora et~al.(2024)]{arora2024intent}
Gaurav Arora, Shreya Jain, and Srujana Merugu. 2024.
\newblock Intent Detection in the Age of {LLMs}.
\newblock In \emph{Proceedings of EMNLP 2024 Industry Track}, pages 1211--1227.

\bibitem[Chen et~al.(2023)]{chen2023frugalgpt}
Lingjiao Chen, Matei Zaharia, and James Zou. 2023.
\newblock {FrugalGPT}: How to Use Large Language Models While Reducing Cost and Improving Performance.
\newblock \emph{arXiv preprint arXiv:2305.05176}.

\bibitem[Larson et~al.(2019)]{larson2019evaluation}
Stefan Larson, Anish Mahendran, Joseph~J. Peper, Christopher Clarke, Andrew Lee, Parker Hill, Jonathan~K. Kummerfeld, Kevin Leach, Michael~A. Laurenzano, Lingjia Tang, and Jason Mars. 2019.
\newblock An Evaluation Dataset for Intent Classification and Out-of-Scope Prediction.
\newblock In \emph{Proceedings of EMNLP-IJCNLP 2019}, pages 1311--1316.

\bibitem[Reimers and Gurevych(2019)]{reimers2019sentencebert}
Nils Reimers and Iryna Gurevych. 2019.
\newblock {Sentence-BERT}: Sentence Embeddings using {Siamese} {BERT}-Networks.
\newblock In \emph{Proceedings of EMNLP-IJCNLP 2019}.

\bibitem[Sierra et~al.(2024)]{sierra2024taubench}
Sierra. 2024.
\newblock $\tau$-bench: A Benchmark for Tool-Agent-User Interaction in Real-World Domains.
\newblock \emph{arXiv preprint arXiv:2406.12045}.

\bibitem[Tunstall et~al.(2022)]{tunstall2022efficient}
Lewis Tunstall, Nils Reimers, Unso~Eun~Seo Jo, Luke Bates, Daniel Korat, Moshe Wasserblat, and Oren Pereg. 2022.
\newblock Efficient Few-Shot Learning Without Prompts.
\newblock \emph{arXiv preprint arXiv:2209.11055}.
\end{thebibliography}

\end{multicols}
\end{document}
